QCL: Added value of differential correlation

### 2011-11-25 inst/doc/article.Rnw
Final commit before Ritsert his comments

\begin{figure}[ht]
  \centering
<<permutation_scores, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
plot(c(0,0.8),c(0,400),type='n',main="QCL scores permutations",ylab="Frequency",xlab="Difference in correlation^2")
hist(qcl_perms[[3]],add=T, col="yellow")
hist(qcl_perms[[2]],add=T, col="red")
hist(qcl_perms[[1]],add=T, col="green")
legend("topright",colnames(ath.metab$phenotypes)[1:3],col=c("yellow","red","green"),lwd=6)
op <- par(cex=1)
@ 
  \caption{QCL scores obtained during permutations (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:histPermAra}}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
<<permutation_scores, fig=TRUE, echo=FALSE, height=3.0>>=
op <- par(cex=0.5)
plot(c(0,0.8),c(0,1000),type='n',main="QCL scores permutations",ylab="Frequency",xlab="Difference in correlation^2")
hist(qcl_perms[[3]],add=T, col="yellow")
hist(qcl_perms[[2]],add=T, col="red")
hist(qcl_perms[[1]],add=T, col="green")
legend("topright",colnames(ath.metab$phenotypes)[1:3],col=c("yellow","red","green"),lwd=6)
op <- par(cex=1)
@ 
  \caption{QCL scores obtained during permutations (A. Thaliana) additional information obtained by QCL mapping, 
  which can be used to reconstruct the underlying genetic architecture.\label{fig:histPermAra}}
\end{figure}
